---
title: "Aim of the project"
author: "Gerko Vink"
date: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---

# Load packages
```{r, message=FALSE}
set.seed(123)
library(mice)
library(dplyr)
library(magrittr)
library(readr)
```

---

# Read in the data
The following data are obtained from [Kaggle](https://www.kaggle.com/uciml/pima-indians-diabetes-database)
```{r}
data <- read_csv("Data/diabetes.csv", 
                 col_types = cols(Pregnancies = col_integer(), 
                                  Glucose = col_integer(), 
                                  BloodPressure = col_integer(), 
                                  SkinThickness = col_integer(), 
                                  Insulin = col_integer(), 
                                  Age = col_integer(), 
                                  Outcome = col_factor(levels = c("1", "0"))))
data %<>% mutate_at(vars(2:8), na_if, y = 0)
imp <- mice(data, m=1, maxit = 35, method = "pmm", print = FALSE)
plot(imp)
data <- complete(imp)
```

---

# Aim
The aim is to mimic the investigations in [this study](https://www.gerkovink.com/need_for_uncertainty/text1.html#simulation) on the *Pima Indians Diabetes* data set. To do so, we follow these steps:

1. Formulate an analysis model
2. Run the analysis model on the data set to obtain the *true* data inference
3. Obtain statistical properties of the *true* data set, such as
- `mean()`
- `variance()`
- `cor()`
- etc. 
4. Plot the distributions of the *true* data set
5. Simulate `nsim = 1000` times the following:
- a. Ampute the data with `ampute()` for a MCAR mechanism
- b. Impute the data $m$ times with `mice` for each of the following imputation methods:
  - mean imputation [`mice.impute.mean`]
  - regression imputation (best value prediction): [`mice.impute.norm.predict`]
  - stochastic regression imputation with $m=1$ [`mice.impute.norm.nob`]
  - stochastic regression imputation with $m=5$ [`mice.impute.norm.nob`]
  - Bayesian linear regression imputation with $m=1$ [`mice.impute.norm`]
  - Bayesian linear regression imputation with $m=5$ [`mice.impute.norm`]
  - Predictive mean matching imputation with $m=1$ [`mice.impute.pmm`]
  - Predictive mean matching imputation with $m=5$ [`mice.impute.pmm`]
- c. calculate the same statistical properties as under (3) on each of the $m$ imputed sets
- d. Run the analysis model on each of the $m$ imputed sets
- e. Combine the $m$ statistics and parameters from (5b) and (5c) into single inferences`
6. Analyze the simulation results by
- a. Calculating the average parameters and statistics over the `nsim = 1000` simulations
- b. Plotting the distributions of the statistics and parameters with e.g. boxplots
- c. Calculating for all statistics and parameters the bootstrap CI.
- d. Calculating for all parameters the parametric CI cf. Rubin's rules.  
- e. Calculating the 95% coverage rates of the parameters and statistics (bootstrap CI and parametric CI)
7. Evaluate the results and determine if and when `mice` would yield valid imputed sets. 

---

# Session
```{r}
sessionInfo()
```

---

End of document